Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-25 SRO_Retest_Analyses.Rmd
cont working on retest exploration

# Loading and matching test and retest datasets

Load original data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
```

Load retest data
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/variables_exhaustive.csv')
```

@@

Extract retest participants from test data

@@

@@

Get list of test retest correlations for all matching (numeric) columns in the test and retest data. Note two caveats:
1. There are still some columns that weren't in both datasets (e.g. two stage)
2. Unlike meaningful variables these variables are not (yet) rid of outliers or log transformed if skewed. This will be detailed below along with its problems.

@@

Distributions of correlations by task vs. survey

@@

Rank order correlations
For tasks
```{r}
cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman)
```

Mean reliability for tasks
```{r}
cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman) %>%
  summarise(mean_pearson = mean(pearson),
            mean_spearman = mean(spearman),
            num_vars = n())
```

For surveys

@@

Mean reliability for surveys
```{r}
cor_df %>%
  filter(task == 'survey') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman) %>%
  summarise(mean_pearson = mean(pearson),
            mean_spearman = mean(spearman),
            num_vars = n())
```

@@

```{r}
clean_retest_data = as.data.frame(apply(retest_data[, matching_dv_columns], 2, remove_outliers))
clean_retest_data = transform_remove_skew(clean_retest_data, matching_dv_columns)
```

@@

```{r}
clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
clean_retest_subs_test_data = transform_remove_skew(retest_subs_test_data, matching_dv_columns)
```

>>>>

# Loading and matching datasets

### Load original data
```{r}
test_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-31-2017/variables_exhaustive.csv')
```

### Load retest data
```{r}
retest_data <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_02-11-2017/variables_exhaustive.csv')
```

@@

### Extract retest participants from test data

@@

### Checks and matching issues

@@

Get list of test retest correlations for all matching (numeric) columns in the test and retest data. Note two caveats:  
**1. There are still some columns that weren't in both datasets listed above (e.g. two stage)**  
**2. Unlike meaningful variables these variables are not (yet) rid of outliers or log transformed if skewed. This will be detailed below along with its problems.**

@@

## Distributions of correlations by task vs. survey

@@

```{r}
cor_df %>%
  group_by(task) %>%
  summarise(mean_pearson = mean(pearson),
            mean_spearman = mean(spearman),
            num_vars = n())
```

### Rank order of correlations

#### For tasks
```{r}
cor_df %>%
  filter(task == 'task') %>%
  select(dv, spearman, pearson) %>%
  arrange(-pearson, -spearman)
```

#### For surveys

@@

@@

```{r warning=FALSE}
clean_retest_data = as.data.frame(apply(retest_data[, matching_dv_columns], 2, remove_outliers))
clean_retest_data = transform_remove_skew(clean_retest_data, matching_dv_columns)
```

@@

```{r warning=FALSE}
clean_retest_subs_test_data = as.data.frame(apply(retest_subs_test_data[, matching_dv_columns], 2, remove_outliers))
clean_retest_subs_test_data = transform_remove_skew(retest_subs_test_data, matching_dv_columns)
```
